---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# erlr

<!-- badges: start -->
[![R-CMD-check](https://github.com/djnavarro/erlr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/djnavarro/erlr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Provides estimation and plotting tools for exposure-response models that use logistic regression for binary responses. It is mostly intended as a convenience package: the core tools are wrappers around `glm()`, and the plotting tools use ggplot2 and patchwork to build typical plots used in exposure-response modelling.

## Installation

You can install the development version of erlr like so:

``` r
pak::pak("djnavarro/erlr")
```

## Example

```{r example}
library(erlr)
library(dplyr)
library(tibble)

lr_data

mod <- lr_model(response_1 ~ exposure_1, lr_data)
mod

lr_data |> 
  lr_plot(exposure_1, response_1) |> 
  lr_plot_add_quantiles(bins = 4) |> 
  lr_plot_add_boxplot(group_by = quartile_1) |> 
  print()

lr_data |> 
  lr_plot(exposure_1, response_1) |> 
  lr_plot_add_quantiles(bins = 4) |> 
  lr_plot_add_jitter_strips(color_by = sex) |> 
  lr_plot_add_boxplot(group_by = quartile_1) |> 
  print()  

lr_data[1:70,] |> 
  lr_plot(exposure_1, response_1) |> 
  lr_plot_add_quantiles(bins = 4) |> 
  lr_plot_add_dotplot_strips(color_by = sex) |> 
  lr_plot_add_boxplot(group_by = quartile_1) |> 
  lr_plot_add_boxplot(group_by = sex) |> 
  print(box_height = 2)

mod <- lr_model(response_1 ~ exposure_1 + sex, lr_data)
sim <- lr_vpc_sim(mod)
sim

lr_vpc_plot(mod, sim, group_by = exposure_1)
lr_vpc_plot(mod, sim, group_by = sex)
```
