---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# erlr

<!-- badges: start -->
[![R-CMD-check](https://github.com/djnavarro/erlr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/djnavarro/erlr/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/djnavarro/erlr/graph/badge.svg)](https://app.codecov.io/gh/djnavarro/erlr)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Provides estimation and plotting tools for exposure-response models that use logistic regression for binary responses. It is mostly intended as a convenience package: the core tools are wrappers around `glm()`, and the plotting tools use ggplot2 and patchwork to build typical plots used in exposure-response modelling.

## Installation

You can install the development version of erlr like so:

``` r
pak::pak("djnavarro/erlr")
```

## Models

```{r}
#| label: lr-model

library(erlr)
library(tibble)

lr_data

mod <- lr_model(ae1 ~ aucss, lr_data)
mod
```

## Plots

```{r}
#| fig-height: 8
#| label: lr-plot

lr_data |> 
  lr_plot(aucss, ae1) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles() |> 
  lr_plot_show_groups(aucss) |> 
  plot()

plt <- lr_data |> 
   lr_plot(aucss, ae2, stratify_by = sex) |> 
   lr_plot_show_model(keep_strata = FALSE) |> 
   lr_plot_show_quantiles(bins = 3) |> 
   lr_plot_show_datastrip() |> 
   lr_plot_show_groups(group_by = c(aucss, treatment), keep_strata = FALSE)

print(plt)
plot(plt)
```

## Stepwise covariate modelling

```{r}
mod1 <- lr_model(ae1 ~ aucss + sex + dose, lr_data)
mod2 <- lr_scm_backward(mod1, candidates = c("sex", "dose"))
lr_scm_history(mod2)
```

## VPC/Simulation

```{r}
#| label: lr-vpc
mod <- lr_model(ae1 ~ aucss + sex, lr_data)
sim <- lr_vpc_sim(mod, seed = 1234)
sim

lr_vpc_plot(mod, sim, group_by = aucss)
lr_vpc_plot(mod, sim, group_by = sex)
```

