---
title: "Modelling"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is the modelling article

```{r setup}
library(erlr)
library(tibble)
```



The core function is `lr_model()`, a very thin wrapper around `glm()` that specifies the family and link function to create a logistic regression. The package comes with a synthetic data set called `lr_data` that we can use:

```{r data-1}
lr_data
```

## Fitting models

Creating a model:

```{r model-1}
mod <- lr_model(formula = ae1 ~ aucss, data = lr_data)
mod
```

## Prediction

The `lr_predict()` function produces model predictions:

```{r predict-1}
pred <- mod |> 
  lr_predict(newdata = tibble(
    aucss = seq(from = 0, to = 1500, by = 100)
  ))
pred
```

The confidence level can be adjusted using the `conf_level` argument

```{r predict-2}
pred <- mod |> 
  lr_predict(
    newdata = tibble(aucss = seq(from = 0, to = 1500, by = 100)), 
    conf_level = 0.8 
  )
pred
```

## Stepwise covariate modelling

There are two functions that control SCM regression, `lr_scm_forward()` and `lr_scm_backward()`:

```{r scm-1}
base_mod <- lr_model(formula = ae1 ~ aucss, data = lr_data)
candidates <- c("sex", "dose", "weight", "age")

final_mod <- base_mod |> 
  lr_scm_forward(candidates, threshold = 0.01, seed = 3425) |> 
  lr_scm_backward(candidates, threshold = 0.001, seed = 9821)

final_mod
```

To extract the log, use `lr_scm_history()`:

```{r}
lr_scm_history(final_mod)
```
