---
title: "Plotting"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is the plotting article

```{r setup}
library(erlr)
```

## Defining plots

Basic usage

```{r basic-plot-1}
lr_data |> 
  lr_plot(exposure = aucss, response = ae1) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles() |> 
  plot()
```

Adding extra components

```{r basic-plot-2}
lr_data |> 
  lr_plot(exposure = aucss, response = ae1) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles() |>
  lr_plot_show_datastrip() |>
  lr_plot_show_groups(group_by = aucss) |> 
  plot()
```

## Stratification

Stratification adds colour across all components

```{r stratification-1}
lr_data |> 
  lr_plot(
    exposure = aucss, 
    response = ae1, 
    stratify_by = sex
  ) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles() |> 
  lr_plot_show_datastrip() |>
  plot()
```

You can suppress stratification for specific components

```{r stratification-2}
lr_data |> 
  lr_plot(
    exposure = aucss, 
    response = ae1, 
    stratify_by = sex
  ) |> 
  lr_plot_show_model(keep_strata = FALSE) |> 
  lr_plot_show_quantiles() |> 
  lr_plot_show_datastrip() |>
  plot()
```

## Model component

Default is `style = "ribbonline"` but you can also draw spaghetti plots to represent parameter uncertainty

```{r model-1}
lr_data |> 
  lr_plot(aucss, ae1) |> 
  lr_plot_show_model(style = "spaghetti") |> 
  lr_plot_show_quantiles() |> 
  plot()
```

## Quantile component

You can modify the number of bins:

```{r quantile-1}
lr_data |> 
  lr_plot(aucss, ae1) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles(bins = 6) |> 
  plot()
```

You can also modify the confidence level for the Clopper-Pearson interval:

```{r quantile-2}
lr_data |> 
  lr_plot(aucss, ae1) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles(bins = 6, conf_level = .8) |> 
  plot()
```

## Strip component


## Group component

Multiple grouping variables are allowed:

```{r group-1}
lr_data |> 
  lr_plot(aucss, ae1) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles() |>
  lr_plot_show_groups(group_by = c(aucss, sex)) |> 
  plot()
```

Stratification propagates to the group component:

```{r group-2}
lr_data |> 
  lr_plot(aucss, ae1, stratify_by = sex) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles() |>
  lr_plot_show_groups(group_by = aucss) |> 
  plot()
```

The default is `style = "boxplot"` but you can also use violin plots:

```{r group-3}
lr_data |> 
  lr_plot(aucss, ae1) |> 
  lr_plot_show_model() |> 
  lr_plot_show_quantiles() |>
  lr_plot_show_groups(group_by = sex, style = "violin") |> 
  plot()
```

